Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-06 paper.tex
Fix typos pointed out by Florent.

\textbf{In this paper, we present a planning algorithm that considers exact models of a humanoid
robot and its environment. It is used to solve navigation and manipulation problems. Our planner 
generates collision-free, statically balanced
geometric paths, i.e. paths such that for any path configurations, the robot is balanced on its
feet with zero speed. We also present a constructive formal proof that these paths can be
approximated by collision-free, dynamically balanced walk trajectories, i.e. trajectories such
that for any trajectory instant, the robot is balanced on at least one foot. Our planner is designed for perfectly modeled indoor
environments, where the floor is horizontal and flat. Also, because we do not compute explicitly footstep
positions at the planning stage, the presented planner is unable to plan motions in which the
robot steps over obstacles. These limitations are discussed in the paper.}

@@

\textbf{This section presents an algorithm for constrained motion
  planning in the configuration space $\mathcal{C}$. In the particular
  case of a humanoid robot which is an under-actuated system,
  $\mathcal{C}=\mathcal{Q} \times SE(3)$, where $\mathcal{Q}$
  represents the kinematic tree actuators and $SE(3)$ corresponds to a
  fictitious floating joint attached to the root of the tree. If the
  robot has $n$ actuated DoFs, then $dim(\mathcal{Q})=n$ and
  $dim(\mathcal{C})=n+6$. A configuration $q$ of $\mathcal{C}$ is said
  to be valid iff, besides being collision-free, it lies on a specific
  submanifold $\manifold$ of $\mathcal{C}$. $\manifold$ is called
  the planning manifold.}

@@

\textbf{We show here how a multiple constraints solver works: its
  purpose is to find the root $q$ of a non-linear $C^1$ function
  $f(q)$ with a tolerance of $\varepsilon$. If we want to find a
  configuration on a manifold $\manifold$, $f(q)$ can be defined as a
  vector function that contains the concatenation of all constraints
  defining $\manifold$. Note that as the intersection of two or more
  manifolds is also a manifold, this constraint solver allows us also
  to generate configurations that lie at the intersection of several
  manifolds.}

>>>>

\textbf{In this paper, we present a planning algorithm that considers
  exact models of a humanoid robot and its environment. It is used to
  solve navigation and manipulation problems. Our planner generates
  collision-free, statically balanced geometric paths, i.e. paths such
  that for any configuration along the path, the robot is balanced on
  its feet with zero speed. We also present a constructive formal
  proof that these paths can be approximated by collision-free,
  dynamically balanced walk trajectories, i.e. trajectories satisfying
  the Newton-Euler equations. Our planner is designed for perfectly
  modeled indoor environments, where the floor is horizontal and
  flat. Also, because we do not compute explicitly footstep positions
  at the planning stage, the presented planner is unable to plan
  motions in which the robot steps over obstacles. These limitations
  are discussed in the paper.}

@@

\textbf{This section presents an algorithm for constrained motion
  planning in the configuration space $\mathcal{C}$. In the particular
  case of a humanoid robot which is an under-actuated system,
  $\mathcal{C}=\mathcal{Q} \times SE(3)$, where $\mathcal{Q}$
  represents the kinematic tree actuators and $SE(3)$ represents the
  position in space of the root of the tree. If the robot has $n$
  actuated DoFs, then $dim(\mathcal{Q})=n$ and
  $dim(\mathcal{C})=n+6$. A configuration $q$ of $\mathcal{C}$ is said
  to be valid iff, besides being collision-free, it lies on a specific
  submanifold $\manifold$ of $\mathcal{C}$. $\manifold$ is called the
  planning manifold.}

@@

\textbf{We show here how a multiple constraint solver works: its
  purpose is to find the root $q$ of a non-linear $C^1$ function
  $f(q)$ with a tolerance of $\varepsilon$. If we want to find a
  configuration on a manifold $\manifold$, $f(q)$ can be defined as a
  vector valued function that contains the concatenation of all
  constraints defining $\manifold$. Note that as the intersection of
  two or more manifolds is also a manifold, this constraint solver
  allows us also to generate configurations that lie at the
  intersection of several manifolds.}
